\pkg{sdmTMB}: An \proglang{R} Package for Fast, Flexible, and User-Friendly Generalized Linear Mixed Effects Models with Spatial and Spatiotemporal Random Fields

### 2023-11-24 doc/paper-jss/sdmTMB-paper.Rnw
slight adjustment to owl fig titles

snow_g1 <- ggplot(data = nao_effect_df) +
  geom_point(aes(X, Y, colour = nao_effect)) +
  geom_sf(data = coast, colour = "gray50") +
  geom_sf(data = lakes, colour = "gray50", fill = NA) +
  coord_sf(
    xlim = c(min(snow2$X), max(snow2$X)),
    ylim = c(min(snow2$Y), max(snow2$Y))
  ) +
  scale_colour_viridis_c(
    limit = c(min(snow$nao_effect_lwr), max(snow$nao_effect_upr)),
    guide = guide_colourbar(direction = "horizontal", title.position = "left")
  ) +
  ggtitle("(a) Median") +
  labs(colour = "Estimated multiplicative effect\nof NAO on Snowy Owl count") +
  theme(legend.position = "top",
          plot.title = element_text(size = 10, hjust = -0.2),
          axis.title = element_blank())

>>>>

snow_g1 <- ggplot(data = nao_effect_df) +
  geom_point(aes(X, Y, colour = nao_effect)) +
  geom_sf(data = coast, colour = "gray50") +
  geom_sf(data = lakes, colour = "gray50", fill = NA) +
  coord_sf(
    xlim = c(min(snow2$X), max(snow2$X)),
    ylim = c(min(snow2$Y), max(snow2$Y))
  ) +
  scale_colour_viridis_c(
    limit = c(min(snow$nao_effect_lwr), max(snow$nao_effect_upr)),
    guide = guide_colourbar(direction = "horizontal", title.position = "left")
  ) +
  ggtitle(paste0("(a) Median multiplicative effect: ", round(min(snow$nao_effect),2), " to ", round(max(snow$nao_effect),2))) +
  labs(colour = "Estimated effect of NAO\non Snowy Owl count") +
  theme(legend.position = "top",
          plot.title = element_text(size = 10, hjust = -0.2),
          axis.title = element_blank())
